Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-04 causal-bandit/icml-2015/setup.tex
Tweaks to related work and set up

The objective of the learner is to minimise the simple regret
\begin{equation}
\label{eq:regret-simple}
	\simpleregret = \mu^* - \E{\mu_{\hat a^*_T}}.
\end{equation}
This is sometimes refered to as a ``pure exploration''~\citep{Bubeck2009} or ``best-arm identification'' problem~\citep{Gabillon2012} and
is most appropriate when the learner has a fixed learning budget after which its policy will be fixed indefintely.

>>>>

The objective of the learner is to minimise the simple regret
\begin{equation}
\label{eq:regret-simple}
	\simpleregret = \mu^* - \E{\mu_{\hat a^*_T}}.
\end{equation}
This is sometimes refered to as a ``pure exploration''~\citep{Bubeck2009} or ``best-arm identification'' problem~\citep{Gabillon2012} and
is most appropriate when, as in drug and policy testing, the learner has a fixed experimental budget after which its policy will be fixed indefintely.
